Temporary Trade Barriers: \\ When Will They End?

### 2016-05-11 presentation.tex
update lobby slide

\begin{frame}
\frametitle{Lobby}
\vskip.2in
Lobby chooses effort to maximize:
\begin{multline*}
  \left\{1-\Pr\left[ \text{TradeWar}(e_b,\bta)\right]\right\} \ \pi(\tau^a) \\
     + \Pr\left[ \text{TradeWar}(e_b,\bta) \right] \left[ \pi(\tau^{\mathit{tw}}) - e_{tw} \right] - e_b
\end{multline*}

\vskip.2in
\begin{itemize}
	\item $e_b$: Lobbying effort for break decision
	\item $e_{tw}$: Lobbying effort for trade-war tariffs
	\item $(\tau^a,\tau^{*a})$: trade agreement tariffs
	\item $\tau^{\textit{ad}}$: tariff equivalent under anti-dumping duties
\end{itemize}

@@

\begin{frame}{Highlight: Separation of Powers}
\pause
\textbf{Legislature}
\pause
\begin{itemize}
	\item Breaks agreement if median legislator prefers $\bm{\tau^{\mathit{tw}}}$ to $\bta$
\end{itemize}

\pause
\vskip.1in
\textbf{Lobby}
\pause
\begin{itemize}[<+->]
	\item Given the $\bta$ it faces, lobby knows what $e_b$ is required to break the agreement
 	\item Lobby pays this $e_b$ if: \hskip.2in $\bm{\pi}(\bm{\tau^{\mathit{tw}}}) \bm{- e_{tw}  - e_b > \pi}(\bm{\tau^a})$
\end{itemize}

\pause
\vskip.13in
\textbf{Executives}
\pause
\begin{itemize}[<+->]
	\item Set $\bta$ to make paying $e_b$ unprofitable
		\begin{itemize}
			\item[$\Rightarrow$] $e_b=0$, agreement remains in force
		\end{itemize}
	\item High tariffs, no lobbying, no trade disruptions
\end{itemize}
\end{frame}

@@

	\pause
  \vskip.2in
  Probability that Legislature breaks agreement: \\
	\pause
  \vskip.1in
    $b(e_b,\bta,\btn,\ta)$ probability median legislator prefers $\tau^{tw}$ to $\tau^a$ for a given $\ta$
\end{frame}

>>>>

\begin{frame}
\frametitle{Lobby}
\vskip.2in
Lobby chooses effort to maximize:
\[
  \left\{1-\Pr\left[ \text{AD Renewal}\right]\right\} \ \pi(\tau^a) + \Pr\left[ \text{AD Renewal} \right]  \pi(\tau^{\mathit{ad}})  - e
\]

\vskip.1in
\begin{itemize}
	\item $e$: Lobbying effort
	\item $\tau^a$: home import tariff under trade agreement
	\item $\tau^{\textit{ad}}$: home import tariff equivalent under anti-dumping duties
\end{itemize}

@@

\begin{frame}{Highlight: Separation of Powers}
\pause
\textbf{Legislature}
\pause
\begin{itemize}
	\item Breaks agreement if median legislator prefers $\tau^{\mathit{ad}}$ to $\tau^a$
\end{itemize}

\pause
\vskip.1in
\textbf{Lobby}
\pause
\begin{itemize}[<+->]
	\item Given the $(\tau^a,\tau^{*a})$ it faces, lobby knows what $e_b$ is required to break the agreement
 	\item Lobby pays this $e_b$ if: \hskip.2in $\pi(\tau^{\mathit{tw}}) - e > \pi(\tau^a)$
\end{itemize}

\pause
\vskip.13in
\textbf{Executives}
\pause
\begin{itemize}[<+->]
	\item Set $(\tau^a,\tau^{*a})$ to make paying $e_b$ unprofitable
		\begin{itemize}
			\item[$\Rightarrow$] $e_b=0$, agreement remains in force
		\end{itemize}
	\item High tariffs, no lobbying, no trade disruptions
\end{itemize}
\end{frame}

@@

	\pause
  \vskip.2in
  Probability that Legislature breaks agreement: \\
	\pause
  \vskip.1in
    $b(e,\tau^a,\tau^{*a},\tau^{\textit{ad}},\ta)$ probability median legislator prefers $\tau^{tw}$ to $\tau^a$ for a given $\ta$
\end{frame}
